### 2015-07-15 fundamentals/intro.tex
emphasizes multiple fidelities toward solution to #118

\Cyclus is a dynamic, agent-based model, which employs a modular architecture,
an open development process, discrete agents, discrete time, and arbitrarily
detailed isotopic resolution of materials. Experience in the broader field of
systems analysis indicates that agent-based modeling enables more flexible
simulation control, without loss of generality
\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling options. This ecosystem is \emph{modular},
being comprised of dynamically loadable, interchangeable, plug-in libraries of fuel cycle component
process physics that vary in their scope, depth, and fidelity. This modularity
allows users and developers to customise \Cyclus to analyze the cases that are
of interest to them, rather than any custom application the simulator was
originally developed to address.  The fundamental concepts of the \Cyclus
nuclear fuel cycle simulator capture these modern insights so that novel
challenges in nuclear fuel cycle analysis can be better addressed.

>>>>

\Cyclus is a dynamic, agent-based model, which employs a modular architecture,
an open development process, discrete agents, discrete time, and arbitrarily
detailed isotopic resolution of materials. Experience in the broader field of
systems analysis indicates that agent-based modeling enables more flexible
simulation control, without loss of generality
\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling options. This ecosystem is \emph{modular},
being comprised of dynamically loadable, interchangeable, plug-in libraries of fuel cycle component
process physics that vary in their scope, depth, and fidelity. This modularity
allows users and developers to customise \Cyclus to analyze the cases that are
of interest to them rather than any custom application the simulator was
originally developed to address. Additionally, that customizability allows
useres and developers to address those cases at the level of fidelity necessary
for their application. The fundamental concepts of the \Cyclus
nuclear fuel cycle simulator capture these modern insights so that novel
challenges in nuclear fuel cycle analysis can be better addressed.
